---
title: "Hakai-Lice-Models-Overview"
author: "Cole"
date: "August 20, 2019"
output: word_document
---
#Preliminary Things

I thought this might be the easiest way to show you all the things without having to copy and paste everything into a word document, so here's an RMD instead lol. 

Necessary packages etc:

```{r, echo=FALSE}
#packages
library(tidyverse)
library(glmmTMB)
library(ggeffects)
library(DHARMa)
library(MuMIn)
library(cowplot)

#data
mainlice <- read.csv("Hakai_lice_data_CB_edits.csv")

#make vars into factors
mainlice$year <- as.factor(mainlice$year);mainlice$collection <- as.factor(mainlice$collection)
```

#Initial Model Set 

The first set of models from this past school year (region removed from initial model and fit by itself)

## Species Level Models

```{r}
#models and dredge them
lepmodspecies.full <- glmmTMB(all.leps ~ spp + year - 1 + (1|collection), 
                         data = mainlice, family=nbinom2)
calmodspecies.full <- glmmTMB(all.cal ~ spp + year - 1 + (1|collection), 
                         data = mainlice, family=nbinom2)

lepmodspecies.full_dredge = MuMIn::dredge(lepmodspecies.full)
calmodspecies.full_dredge = MuMIn::dredge(calmodspecies.full)
lepmodspecies.full_dredge
calmodspecies.full_dredge

```

## Species Level Effects Plots

```{r}
#effects and plot them

calspecieseffects <- ggpredict(calmodspecies.full, terms = c('spp', 'year'))
lepspecieseffects <- ggpredict(lepmodspecies.full, terms = c('spp', 'year'))

lepspecieseffects = lepspecieseffects %>% 
  rename(sal = x, yr = group)

lepspecieseffects$sal = factor(lepspecieseffects$sal, levels = c(1, 2, 3), labels = c('CU', 'PI', 'SO'))

calspecieseffects = calspecieseffects %>% 
  rename(sal = x, yr = group)

calspecieseffects$sal = factor(calspecieseffects$sal, levels = c(1, 2, 3), labels = c('CU', 'PI', 'SO'))

leg_title <- 'Salmon Species'
lepspeciesfullmodplot <- lepspecieseffects %>% 
  group_by(., yr,sal) %>% 
  ggplot(aes(x = sal, y = predicted, colour = sal)) +
  geom_errorbar(aes(ymin=conf.low, ymax = conf.high,width = 0), colour = 'Black')+
  geom_point(size = 4) +
  facet_wrap(~yr,nrow=1,strip.position = "bottom")+
  theme(strip.background = element_blank(), strip.placement = "outside") + 
  scale_color_manual(leg_title,values=c('seagreen2', 'hotpink1', 'steelblue2')) +
  labs(title = "L. salmonis Effects Plot", x = 'Salmon Species/Year', y = 'Average Number of Motile Lice Per Fish')
lepspeciesfullmodplot
calspeciesfullmodplot <- calspecieseffects %>% 
  group_by(., yr,sal) %>% 
  ggplot(aes(x = sal, y = predicted, colour = sal)) +
  geom_errorbar(aes(ymin=conf.low, ymax = conf.high,width = 0), colour = 'Black')+
  geom_point(size = 4) +
  facet_wrap(~yr,nrow=1,strip.position = "bottom")+
  theme(strip.background = element_blank(), strip.placement = "outside") + 
  scale_color_manual(leg_title,values=c('seagreen2', 'hotpink1', 'steelblue2'))+
  labs(title = "C. clemensi Effects Plot", x = 'Salmon Species/Year', y = 'Average Number of Motile Lice Per Fish')
calspeciesfullmodplot
``` 

## Region-Level Models

```{r}
#region-level models
regionlice <- read.csv('Hakai_lice_data_all_fish_CB_edits.csv')

#now lets do it between all three species, by making some sub-dfs first
regionlice$week <- as.factor(regionlice$week); regionlice$year <- as.factor(regionlice$year)
chum.region <- regionlice %>% 
  filter(spp == 'CU')
pink.region <- regionlice %>% 
  filter(spp == 'PI')
sock.region <- regionlice %>% 
  filter(spp == 'SO')

chumrmod.calnb <- glmmTMB(all.cal ~ site.region + year - 1 + (1|week), 
                           data = chum.region, family=nbinom2)
chumrmod.lepsnb <- glmmTMB(all.leps ~ site.region + year - 1 + (1|week), 
                          data = chum.region, family=nbinom2)
pinkrmod.calnb <- glmmTMB(all.cal ~ site.region + year - 1  + (1|week), 
                         data = pink.region, family=nbinom2)
pinkrmod.lepsnb <- glmmTMB(all.leps ~ site.region + year - 1 + (1|week), 
                          data = pink.region, family=nbinom2)
sockrmod.calnb <- glmmTMB(all.cal ~ site.region + year - 1 + (1|week), 
                         data = sock.region, family=nbinom2)
sockrmod.lepsnbsr <- glmmTMB(all.leps ~ site.region - 1 + (1|week), 
                            data = sock.region, family=nbinom2)
summary(chumrmod.calnb); summary(chumrmod.lepsnb); summary(pinkrmod.calnb); summary(pinkrmod.lepsnb); summary(sockrmod.calnb); summary(sockrmod.lepsnbsr)
```

## AIC tables

```{r}
chumcalspeffects <- ggpredict(chumrmod.calnb, terms = c('site.region', 'year'))
chumcalspeffects = chumcalspeffects %>%
  rename(site.region = x, yr = group) %>%
  mutate(lice = 'cal')
chumcalspeffects$site.region = factor(chumcalspeffects$site.region, levels = c(1, 2),
                              labels = c('D', 'J'))

chumlepspeffects <- ggpredict(chumrmod.lepsnb,terms = c('site.region', 'year'))
chumlepspeffects = chumlepspeffects %>%
  rename(site.region = x, yr = group)%>%
  mutate(lice = 'leps')
chumlepspeffects$site.region = factor(chumlepspeffects$site.region, levels = c(1, 2),
                              labels = c('D', 'J'))

pinkcalspeffects <- ggpredict(pinkrmod.calnb, terms = c('site.region', 'year'))
pinkcalspeffects = pinkcalspeffects %>%
  rename(site.region = x, yr = group)%>%
  mutate(lice = 'cal')
pinkcalspeffects$site.region = factor(pinkcalspeffects$site.region, levels = c(1, 2),
                              labels = c('D', 'J'))

pinklepspeffects <- ggpredict(pinkrmod.lepsnb,terms = c('site.region', 'year'))
pinklepspeffects = pinklepspeffects %>%
  rename(site.region = x, yr = group)%>%
  mutate(lice = 'leps')
pinklepspeffects$site.region = factor(pinklepspeffects$site.region, levels = c(1, 2),
                              labels = c('D', 'J'))

sockcalspeffects <- ggpredict(sockrmod.calnb, terms = c('site.region', 'year'))
sockcalspeffects = sockcalspeffects %>%
  rename(site.region = x, yr = group)%>%
  mutate(lice = 'cal')
sockcalspeffects$site.region = factor(sockcalspeffects$site.region, levels = c(1, 2),
                              labels = c('D', 'J'))

socklepspeffects <- ggpredict(sockrmod.lepsnbsr,terms = 'site.region')
socklepspeffects = socklepspeffects %>%
  rename(site.region = x)%>%
  mutate(lice = 'leps')
socklepspeffects$site.region = factor(socklepspeffects$site.region, levels = c(1, 2),
                              labels = c('D', 'J'))

chumeffects = rbind(chumcalspeffects, chumlepspeffects)
pinkeffects = rbind(pinkcalspeffects, pinklepspeffects)

```

## Region Level Effects Plots

```{r}
#make some themes so it all looks nice beside each other
fte_themeSock <- function(){
  color.background = 'white'
  color.grid.major = 'black'
  color.axis.text = 'black'
  color.axis.title = 'black'
  color.title = 'black'
  theme_bw(base_size = 9) +
    theme(panel.background = element_rect(fill=color.background,color = color.background)) +
    theme(plot.background = element_rect(fill = color.background, color = color.background)) +
    theme(panel.border = element_blank()) +
    theme(panel.grid.major = element_blank()) +
    theme(panel.grid.minor = element_blank()) +
    theme(axis.ticks = element_blank()) +
    theme(plot.title = element_text(color = color.title, size = 15, vjust = 1.25)) +
    theme(axis.text.x = element_text(size = 10, color = color.axis.text)) +
    theme(axis.text.y = element_text(size = 10, color = color.axis.text)) +
    theme(axis.title.x = element_text(size = 12, color = color.axis.title, vjust = 0)) +
    theme(axis.title.y = element_text(size = 12, color = color.axis.title, vjust = 1.25)) +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.line.x = element_line(color="black", size = 0.15),
          axis.line.y = element_line(color="black", size = 0.15)) +
    theme(strip.background = element_blank(),
                  strip.placement = 'outside',
          strip.text = element_text(size = 10))+
    theme(legend.position = 'none')
}
fte_themeSock2 <- function(){
  color.background = 'white'
  color.grid.major = 'black'
  color.axis.text = 'black'
  color.axis.title = 'black'
  color.title = 'black'
  theme_bw(base_size = 9) +
    theme(panel.background = element_rect(fill=color.background,color = color.background)) +
    theme(plot.background = element_rect(fill = color.background, color = color.background)) +
    theme(panel.border = element_blank()) +
    theme(panel.grid.major = element_blank()) +
    theme(panel.grid.minor = element_blank()) +
    theme(axis.ticks = element_blank()) +
    theme(plot.title = element_text(color = color.title, size = 15, vjust = 1.25)) +
    theme(axis.text.x = element_text(size = 10, color = color.axis.text)) +
    theme(axis.text.y = element_text(size = 10, color = color.axis.text)) +
    theme(axis.title.x = element_text(size = 12, color = color.axis.title, vjust = 0)) +
    theme(axis.title.y = element_text(size = 12, color = color.axis.title, vjust = 1.25)) +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.line.x = element_line(color="black", size = 0.15),
          axis.line.y = element_line(color="black", size = 0.15)) +
    theme(strip.background = element_blank(),
          strip.placement = 'outside',
          strip.text = element_text(size = 10))+
    theme(legend.position = c(0.9,0.82),
          legend.text = element_text(size = 10),
          legend.title = element_text(size = 10))
}
fte_themeSock3 <- function(){
  color.background = 'white'
  color.grid.major = 'black'
  color.axis.text = 'black'
  color.axis.title = 'black'
  color.title = 'black'
  theme_bw(base_size = 9) +
    theme(panel.background = element_rect(fill=color.background,color = color.background)) +
    theme(plot.background = element_rect(fill = color.background, color = color.background)) +
    theme(panel.border = element_blank()) +
    theme(panel.grid.major = element_blank()) +
    theme(panel.grid.minor = element_blank()) +
    theme(axis.ticks = element_blank()) +
    theme(plot.title = element_text(color = color.title, size = 15, vjust = 1.25)) +
    theme(axis.text.x = element_text(size = 10, color = color.axis.text)) +
    theme(axis.text.y = element_text(size = 10, color = color.axis.text)) +
    theme(axis.title.x = element_text(size = 12, color = color.axis.title,
                                      margin= margin(t = 0.7, r = , b = 0, l = 0, unit = "cm"), vjust = 0)) +
    theme(axis.title.y = element_text(size = 12, color = color.axis.title, vjust = 1.25)) +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.line.x = element_line(color="black", size = 0.15),
          axis.line.y = element_line(color="black", size = 0.15)) +
    theme(strip.background = element_blank(),
          strip.placement = 'outside',
          strip.text = element_text(size = 10))+
    theme(legend.position = 'none')
}
fte_themePink <- function(){
  color.background = 'white'
  color.grid.major = 'black'
  color.axis.text = 'black'
  color.axis.title = 'black'
  color.title = 'black'
  theme_bw(base_size = 9) +
    theme(panel.background = element_rect(fill=color.background,color = color.background)) +
    theme(plot.background = element_rect(fill = color.background, color = color.background)) +
    theme(panel.border = element_blank()) +
    theme(panel.grid.major = element_blank()) +
    theme(panel.grid.minor = element_blank()) +
    theme(axis.ticks = element_blank()) +
    theme(plot.title = element_text(color = color.title, size = 15, vjust = 1.25)) +
    theme(axis.text.x = element_text(size = 10, color = color.axis.text)) +
    theme(axis.text.y = element_blank()) +
    theme(axis.title.x = element_text(size = 12, color = color.axis.title, vjust = 0)) +
    theme(axis.title.y = element_text(size = 12, color = color.axis.title, vjust = 1.25)) +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.line.x = element_line(color="black", size = 0.15),
          axis.line.y = element_line(linetype = 'dashed', color = 'grey75')) +
    theme(strip.background = element_blank(),
          strip.placement = 'outside',
          strip.text = element_text(size = 10))+
    theme(legend.position = 'none')
}
fte_themeChum <- function(){
  color.background = 'white'
  color.grid.major = 'black'
  color.axis.text = 'black'
  color.axis.title = 'black'
  color.title = 'black'
  theme_bw(base_size = 9) +
    theme(panel.background = element_rect(fill=color.background,color = color.background)) +
    theme(plot.background = element_rect(fill = color.background, color = color.background)) +
    theme(panel.border = element_blank()) +
    theme(panel.grid.major = element_blank()) +
    theme(panel.grid.minor = element_blank()) +
    theme(axis.ticks = element_blank()) +
    theme(plot.title = element_text(color = color.title, size = 15, vjust = 1.25)) +
    theme(axis.text.x = element_text(size = 10, color = color.axis.text)) +
    theme(axis.text.y = element_blank()) +
    theme(axis.title.x = element_text(size = 12, color = color.axis.title, vjust = 0)) +
    theme(axis.title.y = element_text(size = 12, color = color.axis.title, vjust = 1.25)) +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.line.x = element_line(color="black", size = 0.15),
          axis.line.y = element_line(linetype = 'dashed', color = 'grey75')) +
    theme(strip.background = element_blank(),
          strip.placement = 'outside',
          strip.text = element_text(size = 10))+
    theme(legend.position = c(0.8,0.82),
          legend.text = element_text(size = 10),
          legend.title = element_text(size = 10))
}

#make the plots
regionestbyspplotchumnb <- chumeffects %>% 
  group_by(.,lice,site.region,yr) %>% 
  ggplot(aes(x=site.region, y = predicted, colour = site.region, shape = lice)) +
  scale_shape_manual(values = c(17,15),labels = c('C. clemensi','L. salmonis'))+
  geom_errorbar(aes(ymin=conf.low, ymax = conf.high, width = 0), position = position_dodge(width = 0.8),colour = 'Black') +
  geom_point(size = 4, position = position_dodge(width=0.8)) +
  facet_wrap(~yr, nrow=1, strip.position = 'bottom')+
  scale_color_manual(values=c('grey60', 'grey20'))+
  labs(title = "Chum Salmon",x = '', y = NULL,shape = 'Lice Species', colour = 'Region')+
  guides(shape = guide_legend(override.aes = list(shape = c(24,22)), type = 'b'))+
  scale_y_continuous(limits = c(0,1.25)) +
  fte_themeChum()
regionestbyspplotchumnb
regionestbyspplotpinknb <- pinkeffects %>% 
  group_by(.,lice,site.region,yr) %>% 
  ggplot(aes(x=site.region, y = predicted, colour = site.region, shape = lice)) +
  scale_shape_manual(values = c(17,15),labels = c('C. clemensi','L. salmonis'))+
  geom_errorbar(aes(ymin=conf.low, ymax = conf.high, width = 0), position = position_dodge(width = 0.8),colour = 'Black') +
  geom_point(size = 4, position = position_dodge(width=0.8)) +
  facet_wrap(~yr, nrow=1, strip.position = 'bottom')+
  theme(strip.background = element_blank(),strip.placement = 'outside') +
  scale_color_manual(values=c('grey60', 'grey20'))+
  labs(title = "Pink Salmon", x = 'Year & Region', y = NULL,shape = 'Lice Species')+
  guides(shape = guide_legend(override.aes = list(shape = c(24,22)), type = 'b'))+
  scale_y_continuous(limits = c(0,1.25)) +
  fte_themePink()
regionestbyspplotpinknb
regionestbyspplotsockcal <- sockcalspeffects %>% 
  group_by(.,lice,site.region,yr) %>% 
  ggplot(aes(x=site.region, y = predicted, colour = site.region, shape = lice)) +
  scale_shape_manual(values = c(17,15),labels = c('C. clemensi','L. salmonis'))+
  geom_errorbar(aes(ymin=conf.low, ymax = conf.high, width = 0), position = position_dodge(width = 0.8),colour = 'Black') +
  geom_point(size = 4, position = position_dodge(width=0.8)) +
  facet_wrap(~yr, nrow=1, strip.position = 'bottom')+
  theme(strip.background = element_blank(),strip.placement = 'outside') +
  scale_color_manual(values=c('grey60', 'grey20'))+
  labs(title = "Sockeye Salmon", x = '', y = 'Average Number of Motile Lice Per Fish',shape = 'Lice Species')+
  guides(shape = guide_legend(override.aes = list(shape = c(24,22)), type = 'b'))+
  scale_y_continuous(limits = c(0,1.25))+
  fte_themeSock()
regionestbyspplotsockcal

regionbothcalsock <- plot_grid(regionestbyspplotsockcal,regionestbyspplotpinknb,regionestbyspplotchumnb,
                          nrow = 1, labels = NULL, rel_widths = c(1,1,1)) 
regionbothcalsock
```

# New Set of Models

## Models (No Crossed Effects)

```{r}
lepmod.yrsrsp <- glmmTMB(all.leps ~ spp + site.region + year - 1 + (1|collection), 
                      data = mainlice, family=nbinom2)
calmod.yrsrsp <- glmmTMB(all.cal ~ spp + site.region + year - 1 + (1|collection), 
                      data = mainlice, family=nbinom2)
```

## AIC tables

```{r}
lepmod.yrsrsp_dredge = MuMIn::dredge(lepmod.yrsrsp)
calmod.yrsrsp_dredge = MuMIn::dredge(calmod.yrsrsp)
lepmod.yrsrsp_dredge
calmod.yrsrsp_dredge
```

## Effects Plots

```{r}
calspeffects <- ggpredict(calmod.yrsrsp, terms = c('spp', 'year', 'site.region'))
lepspeffects <- ggpredict(lepmod.yrsrsp, terms = c('spp', 'year', 'site.region'))

calspeffects = calspeffects %>% 
  rename(sal = x, reg = facet, yr = group)

calspeffects$sal = factor(calspeffects$sal, levels = c(1, 2, 3), labels = c('CU', 'PI', 'SO'))

lepspeffects = lepspeffects %>% 
  rename(sal = x, reg = facet, yr = group)

lepspeffects$sal = factor(lepspeffects$sal, levels = c(1, 2, 3), labels = c('CU', 'PI', 'SO'))

## Make the plots

leg_title <- 'Salmon Species'
leps3fullmodplot <- lepspeffects %>% 
  group_by(., yr,sal,reg) %>% 
  ggplot(aes(x = sal, y = predicted, colour = sal, shape = reg)) +
  scale_shape_manual(values = c(15,17)) +
  geom_errorbar(aes(ymin=conf.low, ymax = conf.high,width = 0), position = position_dodge(width = 0.8),colour = 'Black')+
  geom_point(size = 4,position = position_dodge(width = 0.8)) +
  facet_wrap(~yr,nrow=1,strip.position = "bottom")+
  theme(strip.background = element_blank(), strip.placement = "outside") + 
  scale_color_manual(leg_title,values=c('seagreen2', 'hotpink1', 'steelblue2'))+
  labs(title = "L. salmonis Effects Plot", x = 'Salmon Species/Year', y = 'Average Number of Motile Lice Per Fish') +
  guides(shape = guide_legend(title = 'Region', override.aes = list(shape = c(0,2)), type = 'b'))
leps3fullmodplot
cal3fullmodplot <- calspeffects %>% 
  group_by(., yr,sal,reg) %>% 
  ggplot(aes(x = sal, y = predicted, colour = sal, shape = reg)) +
  scale_shape_manual(values = c(15,17)) +
  geom_errorbar(aes(ymin=conf.low, ymax = conf.high,width = 0), position = position_dodge(width = 0.8),colour = 'Black')+
  geom_point(size = 4,position = position_dodge(width = 0.8)) +
  facet_wrap(~yr,nrow=1,strip.position = "bottom")+
  theme(strip.background = element_blank(), strip.placement = "outside") + 
  scale_color_manual(leg_title,values=c('seagreen2', 'hotpink1', 'steelblue2'))+
  labs(title = "C. clemensi Effects Plot", x = 'Salmon Species/Year', y = 'Average Number of Motile Lice Per Fish') +
  guides(shape = guide_legend(title = 'Region', override.aes = list(shape = c(0,2)), type = 'b'))
cal3fullmodplot
```

## Models (Crossed Effects)

```{r}
lepmod.crossed <- glmmTMB(all.leps ~ spp * site.region + spp * year + 
                            site.region * year + (1 | collection), 
                          data = mainlice, family=nbinom2)
calmod.crossed <- glmmTMB(all.cal ~ spp * site.region + spp * year + 
                            site.region * year + (1 | collection), 
                          data = mainlice, family=nbinom2)
```

## AIC Tables

```{r}
lepmod.crossed_dredge = MuMIn::dredge(lepmod.crossed, subset = (`cond(site.region)` && `cond(year)`))
lepmod.crossed_dredge
calmod.crossed_dredge = MuMIn::dredge(calmod.crossed, subset = (`cond(site.region)` && `cond(year)`))
calmod.crossed_dredge
```

## Effects Plots

```{r}
lepmod.crossed.top <- glmmTMB(all.leps ~ spp + site.region + year + site.region * year - 1 + (1 | collection), 
                      data = mainlice, family=nbinom2)
summary(lepmod.crossed.top)
calmod.crossed.top <- glmmTMB(all.cal ~ year + site.region + spp + spp * site.region + 
                            site.region * year + (1 | collection), 
                          data = mainlice, family=nbinom2)
summary(calmod.crossed.top)

lep_top_effects <- ggpredict(lepmod.crossed.top, terms = c('spp', 'year', 'site.region')) #not sure if I did this right
cal_top_effects <- ggpredict(calmod.crossed.top, terms = c('spp', 'year', 'site.region'))

lep_top_effects = lep_top_effects %>% 
  rename(sal = x, reg = facet, yr = group)
cal_top_effects = cal_top_effects %>% 
  rename(sal = x, reg = facet, yr = group)

lep_top_effects$sal = factor(lep_top_effects$sal, levels = c(1, 2, 3), labels = c('CU', 'PI', 'SO'))
cal_top_effects$sal = factor(cal_top_effects$sal, levels = c(1, 2, 3), labels = c('CU', 'PI', 'SO'))

## Make the plots

leg_title <- 'Salmon Species'
lepsfullmodplot_top <- lep_top_effects %>% 
  group_by(., yr,sal,reg) %>% 
  ggplot(aes(x = sal, y = predicted, colour = sal, shape = reg)) +
  scale_shape_manual(values = c(15,17)) +
  geom_errorbar(aes(ymin=conf.low, ymax = conf.high,width = 0), position = position_dodge(width = 0.8),colour = 'Black')+
  geom_point(size = 4,position = position_dodge(width = 0.8)) +
  facet_wrap(~yr,nrow=1,strip.position = "bottom")+
  theme(strip.background = element_blank(), strip.placement = "outside") + 
  scale_color_manual(leg_title,values=c('seagreen2', 'hotpink1', 'steelblue2'))+
  labs(title = "L. salmonis Effects Plot", x = 'Salmon Species/Year', y = 'Average Number of Motile Lice Per Fish') +
  guides(shape = guide_legend(title = 'Region', override.aes = list(shape = c(0,2)), type = 'b'))
lepsfullmodplot_top
calfullmodplot_top <- cal_top_effects %>% 
  group_by(., yr,sal,reg) %>% 
  ggplot(aes(x = sal, y = predicted, colour = sal, shape = reg)) +
  scale_shape_manual(values = c(15,17)) +
  geom_errorbar(aes(ymin=conf.low, ymax = conf.high,width = 0), position = position_dodge(width = 0.8),colour = 'Black')+
  geom_point(size = 4,position = position_dodge(width = 0.8)) +
  facet_wrap(~yr,nrow=1,strip.position = "bottom")+
  theme(strip.background = element_blank(), strip.placement = "outside") + 
  scale_color_manual(leg_title,values=c('seagreen2', 'hotpink1', 'steelblue2'))+
  labs(title = "C. clemensi Effects Plot", x = 'Salmon Species/Year', y = 'Average Number of Motile Lice Per Fish') +
  guides(shape = guide_legend(title = 'Region', override.aes = list(shape = c(0,2)), type = 'b'))
calfullmodplot_top

```

